Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-10 lineages_18Q3.Rmd
edit G2P level A datasets

```{r}
g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_20181008.tsv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
# g2pA[g2pA == "-1"] <- NA

g2pA_JSON <- data.frame(JSON = g2pA$JSON)
```

>>>>

```{r}
g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.csv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
# g2pA[g2pA == "-1"] <- NA
g2pA$X <- NULL

g2pA_JSON <- data.frame(JSON = g2pA$JSON)

g2pA_noJSON <- g2pA
g2pA_noJSON$JSON <- NULL

# write.table(g2pA, file = "./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
# write.table(g2pA_noJSON, file = "./data_munging/g2pA_noJSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
# write.table(g2pA_JSON, file = "./data_munging/g2pA_JSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
```
